### 2020-01-28 wuhan.tex
big update

We use the gamma approximation framework to first characterize the
amount of uncertainty present in the underlying parameters and then 
to assess the 
degree to which these uncertainties
affect the estimate of $\mathcal R_0$.
Assuming that generation intervals follow a gamma distribution 
with the mean $\bar G$ and the squared coefficient of variation $\kappa$, 
we have
\begin{equation}
\mathcal R_0 = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\end{equation}
This equation demonstrates that a generation-interval distribution
that assumes a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$)
will give a higher estimate of $\mathcal R_0$ for the same value of $r$.

First, we gathered information on estimates of $\mathcal R_0$ and their
assumptions about the underlying generation-interval distributions from preprint servers (e.g., bioRxiv, medRxiv, and SSRN).
Then, we model each parameter ($\mathcal R_0$, $\bar G$, and $\kappa$) with an appropriate probability distribution (either uniform or gamma) that matches the reported estimates or assumptions.
For example, \cite{imaincov} estimated $\mathcal R_0 = 2.5$

>>>>

We use the gamma approximation framework to first characterize the
amount of uncertainty present in the underlying parameters and then 
to assess the 
degree to which these uncertainties
affect the estimate of $\mathcal R_0$.
Assuming that generation intervals follow a gamma distribution 
with the mean $\bar G$ and the squared coefficient of variation $\kappa$, 
we have
\begin{equation}
\mathcal R_0 = \left(1 + \kappa r \bar{G}\right)^{1/\kappa}.
\label{eq:gamma}
\end{equation}
This equation demonstrates that a generation-interval distribution
that assumes a larger mean (higher $\bar{G}$) or is less variable (lower $\kappa$)
will give a higher estimate of $\mathcal R_0$ for the same value of $r$.

First, we gather information on estimates of $\mathcal R_0$ and their
assumptions about the underlying generation-interval distributions from preprint servers (e.g., bioRxiv, medRxiv, and SSRN).
For each study, we model $\mathcal R_0$, $\bar G$, and $\kappa$ with an appropriate probability distribution (either uniform or gamma) that roughly matches the estimated or assumed values and uncertainty ranges.
For example, \cite{imaincov} estimated $\mathcal R_0 = 2.6$ (95\% CI: 1.5--3.5);
we model this parameter as a gamma distribution with mean of 2.6 and a shape parameter of 28, which has a 95.2\% probability of containing a value between 1.5 and 3.5.
Then, we draw 100,000 random samples from these distributions and calculate the exponential growth rate $r$ via the inverse of \eref{gamma}:
\begin{equation}
r = \frac{\mathcal R_0^\kappa - 1}{\kappa \bar{G}}
\end{equation}

To define ranges of appropriate uncertainties for each parameter ($r$, $\bar G$, and $\kappa$),
we use a Bayesian multilevel modeling approach by assuming that all \emph{observed} (i.e., estimated or assumed) parameter values come from the same distribution:
\begin{equation}
\begin{aligned}
r_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_r, \mathrm{shape}=\alpha_r),\\
\bar{G}_i &\sim \mathrm{Gamma}(\mathrm{mean}=\mu_G, \mathrm{shape}=\alpha_G),\\
\kappa_i &\sim \mathrm{Exponential}(\mathrm{mean}=\mu_\kappa),\\
(\mu_r, \alpha_r, \mu_G, \alpha_G, \mu_\kappa) &\sim \mathrm{Gamma}(\mathrm{shape}=0.1, \mathrm{rate}=0.1),
\end{aligned}
\end{equation}
where $i$ represents the index across 6 studies that we consider.
We use an exponential distribution to model $\kappa_i$ to account for the fact that the IDEA model, which \cite{majumderncov} uses, assumes that the generation-interval distribution is fixed ($\kappa = 0$).
Hyperparameters $\mu_r$, $\alpha_r$, $\mu_G$, $\alpha_G$, and $\mu_\kappa$ are estimated with a Markov Chain Monte Carlo (MCMC) by drawing a random set for $r_i$, $\bar{G}_i$, and $\kappa_i$ at each MCMC step from the 100,000 samples that we calculated previously.
We run 4 parallel chains that consist of 100,000 burnin steps and 100,000 sampling steps.
Posterior samples are thinned every 200 steps.
Convergence is assessed by ensuring that the Gelman-Rubin statistic is below 1.01 for all hyperparameters \citep{gelman1992inference}.
